High-Throughput Phenotyping using Computer Vision and Machine Learning \\ \large SMC Data Challenge \#1

### 2023-07-29 paper/main.tex
misspelled Tennessee.. ... . .. ..

\affiliation[fhs]{organization={Farragut High School},
            addressline={11237 Kingston Pike},
            city={Knoxville},
            postcode={37922},
            state={Tennesee},
            country={United States}}

\begin{abstract}
%% Text of abstract
High-throughput phenotyping refers to the non-destructive and efficient evaluation of plant phenotypes. In recent years, it has been coupled with machine learning in order to improve the process of phenotyping plants by increasing efficiency in handling large datasets and developing methods for the extraction of specific traits. Previous studies have developed methods to advance these challenges through the application of deep neural networks in tandem with automated cameras; however, the datasets being studied often excluded physical labels. In this study, we used a dataset provided by Oak Ridge National Laboratory with 1,672 images of Populus Trichocarpa with white labels displaying treatment (control or drought), block, row, position, and genotype. Optical character recognition (OCR) was used to read these labels on the plants, image segmentation techniques in conjunction with machine learning algorithms were used for morphological classifications, machine learning models were used to predict treatment based on those classifications, and analyzed encoded EXIF tags were used for the purpose of finding leaf size and correlations between phenotypes. We found that our OCR model had an accuracy of 94.31\% for non-null text extractions, allowing for the information to be accurately placed in a spreadsheet. Our classification models identified leaf shape, color, and level of brown splotches with an average accuracy of 62.82\%, and plant treatment with an accuracy of 60.08\%. Finally, we identified a few crucial pieces of information absent from the EXIF tags that prevented the assessment of the leaf size. There was also missing information that prevented the assessment of correlations between phenotypes and conditions. However, future studies could improve upon this to allow for the assessment of these features. The use of machine learning and computer vision in high-throughput phenotyping has shown to be effective in analyzing large plant datasets, leading to a more comprehensive phenotype analysis in plants and showing potential in various agricultural and environmental applications.
\end{abstract}

@@

%\tableofcontents

%% \linenumbers

%% main text

@@

To read the text, a pre-trained Optical Character Recognition (OCR) model seemed like the optimal choice. However, there are several high-performing models available for use. The three candidates chosen for this project were \verb|PyTesseract| \citep{lee2017pytesseract}, \verb|EasyOCR| \citep{jaided2020easyocr}, and \verb|PaddleOCR| \citep{du2020ppocr}.

@@

High throughput phenotyping has gained prominence due to its potential in solving a wide variety of agricultural problems. With the world population projected to reach 9.3 billion people by 2050 and a need to produce 60\% more food \citep{silva2012feeding}, it will become crucial for researchers to discover a method for identifying productive genotypes for plant breeding. With computer vision techniques, such as Optical Character Recognition and image processing, and machine learning methods, such as classifiers to predict morphologies and treatments, productivity in the field of plant/crop production will increase rapidly, along with the accurate analysis of plants.

@@

This project is one of the first to utilize \verb|PaddleOCR| \citep{du2020ppocr}, an extremely lightweight and capable Optical Character Recognition model, in the context of reading plant labels. Unlike other approaches, it is resilient to augmentations in data, such as label rotation or minor interruptions in labels.

@@

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections

@@

\begin{center}
	\includegraphics[width=0.45\textwidth]{images/ocr_average_accuracy.png}	
	\captionof{figure}{Average accuracy score for reading the sample dataset for the three OCR models}
	% \label{fig_mom0}%
\end{center}

\begin{center}
	\includegraphics[width=0.45\textwidth]{images/pruned_ocr_average_accuracy.png}	
	\captionof{figure}{Average accuracy score only including non-zero values (only images that were able to be read)}
	% \label{fig_mom0}%
\end{center}

\begin{center}
	\includegraphics[width=0.45\textwidth]{images/ocr_time_taken.png}	
	\captionof{figure}{Total time taken for the three OCR models on the sample dataset}
	% \label{fig_mom0}%
\end{center}

>>>>

\affiliation[fhs]{organization={Farragut High School},
            addressline={11237 Kingston Pike},
            city={Knoxville},
            postcode={37922},
            state={Tennessee},
            country={United States}}

\begin{abstract}
High-throughput phenotyping refers to the non-destructive and efficient evaluation of plant phenotypes. In recent years, it has been coupled with machine learning in order to improve the process of phenotyping plants by increasing efficiency in handling large datasets and developing methods for the extraction of specific traits. Previous studies have developed methods to advance these challenges through the application of deep neural networks in tandem with automated cameras; however, the datasets being studied often excluded physical labels. In this study, we used a dataset provided by Oak Ridge National Laboratory with 1,672 images of Populus Trichocarpa with white labels displaying treatment (control or drought), block, row, position, and genotype. Optical character recognition (OCR) was used to read these labels on the plants, image segmentation techniques in conjunction with machine learning algorithms were used for morphological classifications, machine learning models were used to predict treatment based on those classifications, and analyzed encoded EXIF tags were used for the purpose of finding leaf size and correlations between phenotypes. We found that our OCR model had an accuracy of 94.31\% for non-null text extractions, allowing for the information to be accurately placed in a spreadsheet. Our classification models identified leaf shape, color, and level of brown splotches with an average accuracy of 62.82\%, and plant treatment with an accuracy of 60.08\%. Finally, we identified a few crucial pieces of information absent from the EXIF tags that prevented the assessment of the leaf size. There was also missing information that prevented the assessment of correlations between phenotypes and conditions. However, future studies could improve upon this to allow for the assessment of these features. The use of machine learning and computer vision in high-throughput phenotyping has shown to be effective in analyzing large plant datasets, leading to a more comprehensive phenotype analysis in plants and showing potential in various agricultural and environmental applications.
\end{abstract}

@@

@@

To read the text, a pre-trained optical character recognition (OCR) model seemed like the optimal choice. However, there are several high-performing models available for use. The three candidates chosen for this project were \verb|PyTesseract| \citep{lee2017pytesseract}, \verb|EasyOCR| \citep{jaided2020easyocr}, and \verb|PaddleOCR| \citep{du2020ppocr}.

@@

High throughput phenotyping has gained prominence due to its potential in solving a wide variety of agricultural problems. With the world population projected to reach 9.3 billion people by 2050 and a need to produce 60\% more food \citep{silva2012feeding}, it will become crucial for researchers to discover a method for identifying productive genotypes for plant breeding. With computer vision techniques, such as optical character recognition and image processing, and machine learning methods, such as classifiers to predict morphologies and treatments, productivity in the field of plant/crop production will increase rapidly, along with the accurate analysis of plants.

@@

This project is one of the first to utilize \verb|PaddleOCR| \citep{du2020ppocr}, an extremely lightweight and capable optical character recognition model, in the context of reading plant labels. Unlike other approaches, it is resilient to augmentations in data, such as label rotation or minor interruptions in labels.

@@

@@

\begin{center}
	\includegraphics[width=0.45\textwidth]{images/ocr_average_accuracy.png}	
	\captionof{figure}{Average accuracy score for reading the sample dataset for the three OCR models}
\end{center}

\begin{center}
	\includegraphics[width=0.45\textwidth]{images/pruned_ocr_average_accuracy.png}	
	\captionof{figure}{Average accuracy score only including non-zero values (only images that were able to be read)}
\end{center}

\begin{center}
	\includegraphics[width=0.45\textwidth]{images/ocr_time_taken.png}	
	\captionof{figure}{Total time taken for the three OCR models on the sample dataset}
\end{center}
